Using SIMD and SIMT vectorization to evaluate sparse chemical kinetic Jacobian matrices and thermochemical source terms

### 2018-06-13 paper.tex
add note about pocl not required

\Cref{t:platforms} lists the platforms and vectorization\slash execution patterns that they are capable of running.
The Intel and Nvidia OpenCL runtimes lack implementations of atomic operations on double-precision variables; \revise{\texttt{pyJac} currently needs these} to run deep-vectorized code.
On the other hand, POCL is an open-source OpenCL runtime that works on all CPU types tested here, and does implement these atomic operations.
However, POCL's implicit vectorization module---which uses the LLVM compiler~\cite{Lattner:2004:LCF:977395.977673} to translate OpenCL code to vectorized machine code---typically fails to achieve much, if any, speedup.
\revise{Thus POCL is useful for validation but not necessarily for performance studies.}\todo{should we emphasize here that it isn't needed for pyJac to function properly?}{}
\revise{We will expand upon this discussion} in~\cref{S:future} to highlight future directions.

>>>>

\Cref{t:platforms} lists the platforms and vectorization\slash execution patterns that they are capable of running.
The Intel and Nvidia OpenCL runtimes lack implementations of atomic operations on double-precision variables; \revise{\texttt{pyJac} currently needs these} to run deep-vectorized code.
On the other hand, POCL is an open-source OpenCL runtime that works on all CPU types tested here, and does implement these atomic operations.
However, POCL's implicit vectorization module---which uses the LLVM compiler~\cite{Lattner:2004:LCF:977395.977673} to translate OpenCL code to vectorized machine code---typically fails to achieve much, if any, speedup.
\revise{Thus POCL is useful for validation but not necessarily for performance studies; it is noted that while POCL is currently used by \texttt{pyJac} for unit-testing purposes, it is not a required.}
\revise{We will expand upon this discussion} in~\cref{S:future} to highlight future directions.
